AIR4children: Artificial Intelligence and Robotics for Children

### 2021-02-08 article/tex/submission.tex
adds chios contributions to open teaching materials sections and two references

%

\subsection{Open teaching materials}
[Section to describe open teaching materials, perhaps using non-traditional education systems.]
Serholt 2017 performed studies to quantify the social intereaction 
between robots and children (i.e., gaze, verbal interaction, gestures, 
and facial expressions). However robotics tutors are not yet to the point 
to deal with complex child-robot interactions. 
\cite{Serholt:2017}
A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Conclusions and future work}
[for conclusions and future work].
The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

>>>>

\subsection{Open teaching materials}
Considering the work of Maria Montessori who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}. 
That said, children must develop concentration to develop their learning skills. 
For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
It is through movement and repetition that the child gets experience, allowing him to internalize new concepts. 
One potential way to develip such skills is the help of activities in engigering and robotics. 
Engineering and robotics has demonstrated that young children can experience a range of cognitive and social benefits when these materials are approprietely introduced in development stages [add berg2018, Bers-Horn, 2010; Kazakoff-Bers, 2012)].
Engineering tasks in robotics allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork \cite{elkin2014}.
Similarly, the children development of grasping and understanding mathematical concepts such as number, size, and shape (Bers, 2012; Resnick et al., 1998).

In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
For instance, Elkin et al. (2014) \cite{elkin2014} explained how Robotics can also provide a way to engage children in problem-solving. 
Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
Children who think creatively are curious and open-minded, have a sense of wonder and joy in learning.

Using a variety of teaching materials that combine theory and practice, our workshop has the goal to create experiences to build children’s confidence, develop creativity, teamwork and curiosity.

%[Section to describe open teaching materials, perhaps using non-traditional education systems.]
%Serholt 2017 performed studies to quantify the social intereaction 
%between robots and children (i.e., gaze, verbal interaction, gestures, 
%and facial expressions). However robotics tutors are not yet to the point 
%to deal with complex child-robot interactions. 
%\cite{Serholt:2017}

\section{Conclusions and future work}
[for conclusions and future work].
The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.
A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}
